%---------------------------------------------------------------------------
%	SECTION TITLE
%---------------------------------------------------------------------------

\cvsection{Research Experience}

%--------------------------------------------------------------------------
%	SECTION CONTENT
%---------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cvresearch
{Center for Nonlinear Science, Georgia Institute of Technology}
{Atlanta, GA, USA}
{Jun. 2013 -- May. 2017}
{Role : Research Assistant \quad Adviser : Prof. Predrag Cvitanovi\'c }
{
	\cvresearchitem
	{Computation of Floquet vectors in Kuramoto-Sivashinsky system}
	{The Floquet multipliers of Periodic orbits in high dimensional system usually spans a large orders of magnitudes. The periodic eigendecomposition is the right tool to obtain Floquet spectrum and vectors to high accuracy. See paper[2] for more detail.}
}
\cventry
{\textbf{Research topic :} \emph{Investigation of the local dimension of inertial manifolds in chaotic systems}}
{}{}
{2014 -- 2015}
{
  \begin{cvitems}
    %\item {\textbf{Adviser :} Prof. Predrag Cvitanovi\'c}
    \item {\textbf{Main result:} By studying the shadowing cases of periodic orbits in
        Kuramoto-Sivashinsky system, we show strong evidence that the inertial manifold has
        dimension 8. see paper [1] for more details.}
  \end{cvitems}
}

\cventry
{\textbf{Research topic :} \emph{Symbolic dynamics in symmetry reduced 1-d Kuramoto-Sivashinsky system}}
{}{}
{2015 -- Present}
{
  \begin{cvitems}
      \item {In the symmetry reduced state space, the attractor of  1-d Kuramoto-Sivashinsky system
          is low dimensional. By constructing appropriate Poincar\'e section, we propose to obtain the
          symbolic dynamics. }
  \end{cvitems}
}


\cvresearch
{School of Mathematics, Georgia Tech} 
{Atlanta, GA, USA}
{Spring 2016} 
{Role : Cooperation with Prof. Sung Ha Kang from Math department}
	{}
	\cventry
{\textbf{Research topic :} \emph{Integration of soliton explosion with local error control in cubic quintic 
  Ginzburg-Landau system}}
	{}{}{}
{
  \begin{cvitems}
  \item {\textbf{Main result:}  Study the performance of exponential integrator in Ginzburg-Landau system,
      and add time step control into a few popular exponential integrators. See paper [3].}
  \end{cvitems}
}


% \cventry 
% {Teaching Assistant}
% {Center for Nonlinear Science, School of Physics,
%   Georgia Institute of Technology}
% {Atlanta, GA, USA}
% {2012 -- 2013}
% {
%   \begin{cvitems}
%   \item { Guide undergraduate students in physical experiments.}
%   \end{cvitems}
% }


%------------------------------------------------

\end{cventries}
