%---------------------------------------------------------------------------
%	SECTION TITLE
%---------------------------------------------------------------------------

\cvsection{Industry Experience}

%---------------------------------------------------------------------------
%	SECTION CONTENT
%---------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
% {Web developer @ online course: \emph{Geometry of Chaos}}
% {Atlanta, GA, USA}
% {Jan. 2015 -- Jul. 2015}
% {www.chaosbook.org/course1}
% {
% 	\cvindustryitem
% 	{Design and implement online autograder}
% 	{Django in Python}
% 	{{\bullet} Email back grades automatically {\bullet} Publish grade statistics {\bullet} Grade panel for course instructors}
% }

%------------------------------------------------
\company{Airbnb}{Software Engineer}{San Francisco, CA, USA}{May. 2017 -- Present} 
\team{Search ranking team}{Mar. 2019 -- Present}

\vspace{-2em}

\begin{itemize}[leftmargin=5ex, nosep, noitemsep]
\item \researchitemstyle{Main responsibility:} 
	\begin{spacing}{0.5}
		\begin{itemize}[leftmargin=2ex, nosep, noitemsep]
			\item \descriptionstyle{Migrate user profiler features for a customized KV store to HBase and use Apache Flink for better streaming performance.}
			\item \descriptionstyle{Prepare training data of big size by daily scheduled spark jobs.}
		\end{itemize}
	\end{spacing}
\item \researchitemstyle{Used framework \& tools:} 
	\descriptionstyle{Spark, Hive, Airflow, Scala}	
\end{itemize}

\vspace{-1em}

\team{Home infra team}{May. 2017 -- Feb. 2019}
\vspace{-2em}
\begin{itemize}[leftmargin=5ex] % [leftmargin=2ex, nosep, noitemsep]
\categoryitem{Main contributions:}
	\begin{spacing}{0.5}
		\begin{itemize}[leftmargin=2ex, nosep, noitemsep]
			\workitem{Lead the project of building the next generation of review service, i.e., Ebert2.0, for Airbnb. 
				This is also a review platform that supports homes reviews, experience reviews, LuxuryRetreat reviews and so on.
				We have successfully migrated 340+M reviews and 1B+ review categories to new review schema without downtime, and 
				there were only 3 inconsistent records after migration.}
			\workitem{Collaborate with storage team to setup the derived data store to provide review aggregated data, 
				which improved the tail latency by half (P95 latency from 85ms to 45ms).}
			\workitem{Migrate AWS EC2 review Elasticsearch cluster to AWS managed ES cluster. Also upgrade ES version from 1.4.5 to 6.2.1}
			\workitem{Maintaining current review service add and new features such as group companion review, highlighted reviews on checkout page, review ranking logic on production page, reviews pipelines for SEO purpose and so on.}
		\end{itemize}
	\end{spacing}
\item \researchitemstyle{Core metrics\&features:} 
	\begin{spacing}{0.3} 
    \begin{itemize}[leftmargin=2ex, nosep, noitemsep]   
    \item \researchitemstyle{QPS:} 
    	\descriptionstyle{Average: 12K. Peak: 15K. Traffic comes from room description page, user profile page, checkout page and so on.}
    \item \researchitemstyle{Latency:} 
    	\descriptionstyle{Overall, P95: $\sim$45ms; $\sim$P99: $\sim$80ms; P999: $\sim$250ms. Different endpoints have different latency.}
    \item \researchitemstyle{Features:}
    	\descriptionstyle{{\bullet} Mcrouter cache enabled {\bullet} Horizontal scalable {\bullet} Accompanied by mutation publisher}
    \end{itemize}
  \end{spacing}
\item \researchitemstyle{Used framework \& tools:} 
	\descriptionstyle{Dropwizard, Chef, Airflow, Elasticsearch, Mcrouter Cache, Powergrid(multithreading)}
\end{itemize}


% \cvindustry
% {Software Engineer @ Airbnb}{San Francisco, CA, USA}{May. 2017 -- Present}
% {Home Infra team}
% {
% 	\cvindustryitem
% 	{Build and maintain \underline{Ebert} (the review service) for \emph{airbnb.com}. Being the only person developing this company-wide service.}
% 	{Dropwizard & Chef}
% 	{{\bullet} Mcrouter cache enabled {\bullet} Horizontal scalable {\bullet} Accompanied by mutation publisher}
% }

\end{cventries}
